Races with hyper3 objects

### 2022-06-30 inst/race3.Rmd
more work on false null
typo

The $p$-value is about 0.81, exceeding 0.05; thus we have no strong
evidence to reject the null of $a=\frac{1}{2}$.  Further, we can use
either analytical or numerical methods to find a credible interval.
With an $n$-unit of support criterion the analytical solution to
$\mathcal{S}(p)=-2$ is given by defining $X=\log(3-2\sqrt{2})-n$ and
solving $p(1-p)/(1+p)=X$, or
$p_\pm=\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the
lower and upper limits of the credible interval.  Graphically:

@@

>>>>

The $p$-value is about 0.81, exceeding 0.05; thus we have no strong
evidence to reject the null of $a=\frac{1}{2}$.  Further, we can use
either analytical or numerical methods to find a credible interval.
With an $n$-unit of support criterion the analytical solution to
$\mathcal{S}(p)=-n$ is given by defining $X=\log(3-2\sqrt{2})-n$ and
solving $p(1-p)/(1+p)=X$, or
$p_\pm=\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the
lower and upper limits of the credible interval.  Graphically:

@@

# Estimation of strength

We will try some random simulation where the strengths of the competitors is known:

```{r,label=randomsimknownstrength,cache=TRUE}

es <- replicate(100,maxp(ordervec2supp3(rrace3(pn=c(a=10,b=10),ps=c(a=1/2,b=1/2))))[1])
```

```{r,label=showestimates}
hist(es)
abline(v=1/2,lwd=5)
```
